[Result, but poetic]: Does LLM Use Improve Data Science Education?

### 2024-07-19 paper/paper.qmd
finished code to clean program names; finished code for ai_use_cases; visualized GPA and year distribution; data clean!

```{r}
#Histogram of GPA

@@

>>>>

```{r fig-gpa-hist}
#Histogram of GPA

@@

```{r fig-year-bar}
#Bar plot of year
raw_data |> ggplot(aes(x = year)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Distribution of Students by Year",
       x = "Year",
       y = "Frequency") +
  theme_minimal()

```{r fig-writingease-bar}
#Bar plot of writing ease
raw_data |> ggplot(aes(x = writing_is_easy_for_me)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Distribution of Responses to AI Schoolwork Appropriateness",
       x = "Response",
       y = "Frequency") +
  theme_minimal()  # <- fix the labels as they encroach. NO it broke.
